Inference for Numerical Data

### 2018-10-30 DATA606/Inference for Numerical Data.Rmd
More work

(a) Write hypotheses for evaluating whether the average number of hours worked varies across the five groups. **H0: $\mu$1 = $\mu$2 = $\mu$3 = $\mu$4 = $\mu$5 and HA: The average varies across some or all groups.**

@@

|           |    Df   | Sum Sq  | Mean Sq | F value | Pr(>F) |
|-----------|---------|---------|---------|---------|--------|
| degree    |**     **| ** **   | 501.54  | ** **   | 0.0682 |
| Residuals |**     **| 267,382 | ** **   |         |        |
| Total     |**1,172**| ** **   |         |         |        |

>>>>

(a) Write hypotheses for evaluating whether the average number of hours worked varies across the five groups. **H0: $\mu_1$ = $\mu_2$ = $\mu_3$ = $\mu_4$ = $\mu_5$ and HA: The average varies across some or all groups.**

@@

|           |    Df   | Sum Sq  | Mean Sq | F value | Pr(>F) |
|-----------|---------|---------|---------|---------|--------|
| degree    |         |         | 501.54  |         | 0.0682 |
| Residuals |         | 267,382 |         |         |        |
| Total     |**1,172**|         |         |         |        |
